\sectionTitle{Publications}{\faBook}

\begin{pub}
\normalsize

\pubentry{ACIIDS 2026 (CORE~B)}{
\textbf{Thi Minh Chau Nguyen}, Minh Hieu Nguyen, Duc Anh Nguyen, Xuan Huong Tran, Quoc Viet Hung Nguyen, Thanh Trung Huynh.
\textbf{LUMOS: LLM-Driven Contrastive Federated Sequential Recommendation}.
}
% \pubentry{}{\emph{Contribution:} Participated in the development of a federated sequential recommendation framework where Large Language Models (LLMs) are used as on-device behavioural generators. Contributed to the design and experimentation of a tri-view contrastive learning mechanism that leverages predictive, paraphrased, and counterfactual sequences to address data sparsity and improve next-item prediction.}
\pubentry{}{
\emph{Contributions:}
\begin{itemize}
    \item Participated in the development of a federated sequential recommendation framework where Large Language Models (LLMs) are used as on-device behavioural generators.
    \item Contributed to the design and experimentation of a tri-view contrastive learning mechanism leveraging predictive, paraphrased, and counterfactual sequences.
    \item Addressed data sparsity and enhanced next-item prediction performance through the proposed methodology.
\end{itemize}
}

\pubentry{DAIS 2026 (CORE~C)}{
\textbf{Thi Minh Chau Nguyen}, Dong Duc Anh Nguyen, Duc Anh Nguyen, Van Ho-Long, Thanh Trung Huynh, Zhao Ren.
\textbf{Improving Federated Graph Recommendation with Semantic Guidance}.
}
\pubentry{}{
\emph{Contributions:}
\begin{itemize}
    \item Contributed to the development of a semantic--structural federated graph recommendation framework.
    \item Leveraged LLM-derived semantic embeddings to guide the alignment of community-level structural representations across clients.
    \item Participated in experimental evaluation and visualization demonstrating improved robustness under non-IID data distributions.
\end{itemize}
}
\end{pub}