\sectionTitle{Work Experience}{\faSuitcase}

\begin{experiences}

  \experience
    {Present}
    {Research Assistant}{VinUniversity}{Vietnam}
    {May 2024}
    {
      \begin{itemize}\raggedright\sloppy
        \item Contribute to research projects in Artificial Intelligence, with a focus on recommender systems and applied machine learning.
        \item Conduct literature reviews, data analysis, and experimental implementation to support academic publications.
        \item Collaborate with senior researchers and interdisciplinary teams in preparing research manuscripts and technical reports.
        \item Support the development of AI-driven solutions for real-world applications in marketing and economic contexts.
      \end{itemize}
    }
    {}

  \emptySeparator

  \experience
    {May 2024}
    {Charter Executive}{Bamboo Airways Joint Stock Company}{Vietnam}
    {Jun 2021}
    {
      \begin{itemize}
        \item Negotiated and coordinated charter flight operations with domestic and international partners.
        \item Analysed market demand and proposed competitive pricing strategies for charter services.
        \item Prepared and managed contractual agreements while coordinating with multiple internal and external stakeholders.
        \item Developed strong skills in project coordination, communication, and problem-solving within a dynamic business environment.
      \end{itemize}
    }
    {}

  \emptySeparator

  \experience
    {Apr 2021}
    {Operation Executive}{DHT Aviation}{Vietnam}
    {Sep 2020}
    {
      \begin{itemize}
        \item Represented foreign airlines in Vietnam and maintained communication with international partners.
        \item Coordinated operational activities with handling agents to ensure efficient service delivery.
        \item Supported organisational planning and execution of aviation-related services.
      \end{itemize}
    }
    {}

  \emptySeparator

  \experience
    {Aug 2020}
    {Charter Executive}{Bamboo Airways Joint Stock Company}{Vietnam}
    {Jun 2019}
    {
      \begin{itemize}
        \item Managed communication with partners and supported the coordination of charter flight operations.
        \item Assisted in pricing calculations and preparation of contractual documentation.
        \item Collaborated with cross-functional teams to ensure smooth operational processes.
      \end{itemize}
    }
    {}

  \emptySeparator

  \experience
    {Jun 2019}
    {Student Service Officer}{Cleverlearn Vietnam}{Vietnam}
    {Jan 2018}
    {
      \begin{itemize}
        \item Recruited and trained teaching assistants while supervising their working processes.
        \item Performed administrative tasks related to academic and training activities.
        \item Participated in the observation and improvement of teaching quality.
        \item Provided academic and administrative support to students.
      \end{itemize}
    }
    {}

\end{experiences}