% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
\sectionTitle{Summary}{\faBook}

Graduated with a Bachelor’s degree in International Economics, I developed a strong interest in understanding how data can support strategic decision-making in business and marketing. Through my professional experience in the aviation industry, I gained practical insights into customer behavior, pricing strategies, and market dynamics. These experiences gradually led me to explore how \textbf{Artificial Intelligence} can be applied to solve real-world economic and marketing problems.

Currently, I am working as a \textbf{Research Assistant at VinUniversity}, where I contribute to research projects in \textbf{recommender systems and applied machine learning}. This role has strengthened my skills in literature review, data analysis, and experimental implementation, and has allowed me to transition from an economics background into the field of AI research.

\textbf{Research:} I am a co-author of two peer-reviewed international conference publications:
\begin{itemize}
    \item \textit{LUMOS: LLM-Driven Contrastive Federated Sequential Recommendation}, ACIIDS 2026 (Rank B).
    \item \textit{Improving Federated Graph Recommendation with Semantic Guidance}, DAIS 2026 (Rank C).
\end{itemize}
These works reflect my growing engagement in academic research and my ability to collaborate within interdisciplinary teams.

\textbf{Career Objective:} I aim to pursue a PhD at Griffith University to further develop AI-driven approaches for addressing practical challenges in \textbf{marketing and economic systems}. My long-term goal is to bridge the gap between economic theory and intelligent data-driven solutions that can create meaningful impact in real-world applications.